\documentclass[a4paper,11pt]{book}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\title{Aki Gikendaasowin}
\author{Thuja Occidentalis}

\begin{document}

\maketitle
\tableofcontents

\chapter{Differential Calculus}
\section{The $ \Delta x $ Method}
\LARGE 
\[ \lim_{\Delta x \to 0} \frac{f(x + \Delta x) - f(x)}{\Delta x} \]

\paragraph{Example}
\begin{enumerate}
  \item \[ f(x) = x^2 \]
  \item \[ f(x + \Delta x) = (x + \Delta x)^2 \]
  \item \[ f'(x) = \frac{(x + \Delta x)^2 - x^2}{\Delta x} \]
  \item \[ f'(x) = \lim_{\Delta x \to 0} \frac{x^2 + 2x\Delta x + (\Delta x)^2 - x^2}{\Delta x} \]
  \item \[ f'(x) = \lim_{\Delta x \to 0} \frac{2x\Delta x + (\Delta x)^2}{\Delta x} \]
  \item \[ f'(x) = \lim_{\Delta x \to 0} \frac{\Delta x (2x +\Delta x)}{\Delta x} \]  
  \item \[ f'(x) = \lim_{\Delta x \to 0} (2x +\Delta x) \]
  \item \[ f'(x) = 2x + 0 \]
  \item \[ f'(x) = 2x \]
  \large 
  \textit{\textbf{The derivative of the function $ x^2 $ is 2x}}
\end{enumerate}

\subsubsection{What is the Derivative?}
\normalsize 
When we find the derivative, we find an expression that will yield the slope of the tangent line drawn at any point on the function.

To find the derivative of the tangent line at x = 2, we simply insert x = 2 into the derivative:
\LARGE 
\[ f'(x) = 2x \]
\[ f'(2) = 2(2) \]
\[ f'(2) = 4 \]






\section{Simple Polynomials}
\paragraph{Finding the Derrivative of Simple Polynomials}
\normalsize 
\begin{enumerate}
  \item Term by term, take the exponent on the term, bring it down, and make it a coefficient in front of the term.
  \item Lower the original exponent by one power
  \item The derivative of any constant is zero
\end{enumerate}

\subsubsection{Simple Polynomials:}
\LARGE 
\[ f(x) = ax^n + {bx}^{n-1} + ... \]
\[ f'(x) = {nax}^{n-1} + {(n-1)bx}^{n-2} + ... \]

\subsubsection{Example 1}
\LARGE 
\begin{enumerate}
  \item \[ f(x) = 3x^2 + 4 \]
  \item \[ f'(x) = {2(3)x}^{2-1} + 4 \]
  \item \[ f'(x) = 6x + 0 \]
  \item \[ f'(x) = 6x \] 
\end{enumerate}
\normalsize 


\subsubsection{Example 2}
\LARGE 
\begin{enumerate}
  \item \[ f(x) = \sqrt[3]{x^2} + \frac{5}{x^2} \]
  \item \[ f'(x) ={x}^{\frac{2}{3}} + {5x}^{-2} \]
  \item \[ f'(x) = {\frac{2}{3}x}^{\frac{2}{3}-1} + {5(-2)x}^{-2-1} \]
\item \[ f'(x) = {\frac{2}{3}x}^{-\frac{1}{3}} - {10x}^{-3} \]
\end{enumerate}
\normalsize 









\section{Sine Function}
\paragraph{Finding the Derrivative of the Sine Function}
\normalsize 
\begin{enumerate}
  \item Take the argument of the sine function (whatever is inside the parentheses) and make it the argument of the cosine function.
  \item Multiply in front of the cosine function by the derivative of whatever is inside the parentheses
\end{enumerate}

\subsubsection{Sine functions:}
\LARGE 
\[ f(x) = sin[g(x)] \]
\[ f'(x) = g'(x)cos[g(x)] \]

\subsubsection{Example}
\LARGE 
\begin{enumerate}
  \item \[ f(x) = sin(3x^2 + 4x) \]
  \item \[ f'(x) = (6x + 4)cos(3x^2 + 4x) \]
\end{enumerate}
\normalsize 









\section{Cosine Function}
\paragraph{Finding the Derrivative of the Cosine Function}
\normalsize 
\begin{enumerate}
  \item Take the argument of the sine function (whatever is inside the parentheses) and make it the argument of the sine function.
  \item Multiply in front of the sine function by the derivative of whatever is inside the parentheses
  \item As a last step, multiply your answer by negative 1
\end{enumerate}

\subsubsection{Sine functions:}
\LARGE 
\[ f(x) = cos[g(x)] \]
\[ f'(x) = -g'(x)sin[g(x)] \]

\subsubsection{Example}
\LARGE 
\begin{enumerate}
  \item \[ f(x) = cos(5x^2 + 6x) \]
  \item \[ f'(x) = -(10x + 6)sin(5x^2 + 6x) \]
\end{enumerate}
\normalsize 










\section{Exponential Function}
\paragraph{Finding the Derrivative of Exponential Functions}
\normalsize 
\begin{enumerate}
  \item Recopy the exponential function \textit{without changing the function in any way.}
  \item Multiply in front of the function by the derivative of the exponent to which e has been raised.
\end{enumerate}

\subsubsection{Exponential functionss:}
\LARGE 
\[ f(x) = {e}^{g(x)} \]
\[ f'(x) = {g'(x)e}^{g(x)} \]

\subsubsection{Example}
\LARGE 
\begin{enumerate}
  \item \[ f(x) = {e}^{2x+1} \]
  \item \[ f'(x) = {2e}^{2x+1} \]
\end{enumerate}
\normalsize 
To find the slope of the tangent line at x = 1, we substitute 1 in for x.
\LARGE 
\[ f'(x) = {2e}^{2x+1} \]
\[ f'(1) = {2e}^{2(1) + 1} \]
\[ f'(1) = {2e}^{3} \]
\[ f'(1) = 40.17 \]
\normalsize 










\section{Natural Logarithm}
\paragraph{Finding the Derrivative of the Natural Logarithm}
\normalsize 
\begin{enumerate}
  \item Take the argument of the logarithm and place it under 1.
  \item Multiply the fraction from Step 1 by the derivative of the argument.
\end{enumerate}

\subsubsection{Natural Logarithm:}
\LARGE 
\[ f(x) = ln[g(x)] \]
\[ f'(x) = \frac{g'(x)}{g(x)} \]

\subsubsection{Example}
\LARGE 
\begin{enumerate}
  \item \[ f(x) = ln(4x + 1) \]
  \item \[ f'(x) = 4\cdot \frac{1}{4x + 1} \]
  \item \[ f'(x) = \frac{4}{4x + 1} \]
\end{enumerate}
\normalsize 










\section{The Product Rule}
\subsubsection{Finding the Derrivative using The Product Rule}
\normalsize 
We use the \textit{Product Rule} whenever we have two expressions multiplied together.
\\
\\

We can find the derivative of a function that is a product of two expressions by taking the first expression times the derivative of the second expression, plus the second expression times the derivative of the first expression.

\subsubsection{The Product  of Two Functions:}
\LARGE 
\[ f(x) = g(x)h(x) \]
\[ f'(x) = g(x)h'(x) + h(x)g'(x) \]

\subsubsection{Example}
\LARGE 
\begin{enumerate}
  \item \[ f(x) = (3x^2 + 4x + 8)(7x^3 + 5x^2) \]
  \item \[ f'(x) = (3x^2 + 4x + 8)(21x^2 + 10x) + (7x^3 + 5x^2)(6x + 4) \]
\end{enumerate}
\normalsize 










\section{The Quotient Rule}
\subsubsection{Finding the Derrivative using The Quotient Rule}


\normalsize 
To find the derivative of a function that contains two expressions divided by one another, take the denominator times the derivative of the numerator, minus the numerator times the derivative of the denominator, all over the denominator squared.

\subsubsection{The Quotient  of Two Functions:}
\LARGE 
\[ f(x) = \frac{g(x)}{h(x)} \]
\[ f'(x) = \frac{h(x)g'(x)-g(x)h'(x)}{[h(x)]^2} \]

\subsubsection{Example}
\LARGE 
\begin{enumerate}
  \item \[ f(x) = \frac{4x^3 + 3x^2 - 7x}{5x^2 + 4x} \]
  \item \large \[ f(x) = \frac{(5x^2 + 4x)(12x^2 + 6x - 7) - (4x^3 + 3x^2 - 7x)(10x + 4))}{(5x^2 + 4x)^2} \]
\end{enumerate}
\normalsize 


\end{document}
